Intro Seminar

### 2017-03-13 doc/seminar2017.Rmd
Subject characterization table using complete data

```{r dsSetup}
ds <- project_data
# 
# dsBase <- ds %>% 
#   dplyr::filter(fVN == "Baseline")
# 
# dsComplete <- ds %>% 
#   dplyr::group_by(SID) %>%
#   dplyr::filter(n() == 3) %>%
#   dplyr::ungroup()
```

@@

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR"))
  # knitr::kable()
```

>>>>

```{r dsSetup}
ds <- project_data
# 
# dsBase <- ds %>% 
#   dplyr::filter(fVN == "Baseline")
# 
dsComplete <- ds %>%
  dplyr::group_by(SID) %>%
  dplyr::filter(n() == 3) %>%
  dplyr::ungroup()
```

@@

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("fVN"),
  data = dsComplete,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "UrineMicroalbumin", 
                      "UrineCreatinine", 
                      "ACR"))
  # knitr::kable()
```
